Figure 1a

### 2017-11-20 inst/cellular_localization/cellular_localization.Rmd
starting to change Rmds to use new fileMap function

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

@@

url <- "suppFigure1e_cellularLocalization.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

>>>>

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

@@

url <- fileMap(type = "rds")["suppFigure1e"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

### 2017-11-20 inst/mir34a_locus/mir34a_locus.Rmd
starting to change Rmds to use new fileMap function

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

@@

url <- "figure1a_miR34aLocus/miR34aLocus_hg38.png"
knitr::include_graphics(file.path(projectUrl, url))

>>>>

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

@@

url <- "mir34a_locus/mir34a_locus_hg38.png"
knitr::include_graphics(file.path(projectUrl, url))
